### 2024-08-27 parts/correction.tex
integer binomial polynomials

    \textbf{Base case: $k = 1$.}
    Let us show that $f \circ q$ is
    actually a constant (positive) function (and in particular a \kl{natural binomial polynomial}), as for
    all $n_1, \dots, n_p \geq 1$,
    \begin{align*}
        f(q(n_1, \dots, n_p))
        &\eqdef \pi\left(\mu(q(n_1, \dots, n_p))\right) \\
        &\eqdef \pi\left(\mu(\alpha_0 \prod_{i = 1}^p u_i^{\omega n_i} \alpha_i)\right)
        \\
        &= \pi\left(\mu(\alpha_0) \prod_{i = 1}^p \mu(u_i)^{\omega n_i} \mu(\alpha_i)\right) 
        & \text{ morphism }
        \\
        &= \pi\left(\mu(\alpha_0) \prod_{i = 1}^p \mu(u_i) \mu(\alpha_i)\right)
        & \text{ idempotent and } n_i \geq 1 \\
        &= c \geq 0
    \end{align*}

@@

    With all of this preliminary work done, we are now ready to conclude by
    simply unrolling the definition of 
    a function
    $f$ defined using a \kl{production function}
    $\pi \colon M^{k+1} \to \Nat$.
    In the following equations, we omit the precise
    range for the sum over $(\ell, r, b)$ to save space.
    Similarly, we will use 
    $q_{\ell,r}(X_1, \dots, X_{p-\ell+1})
    \defined q_{\ell,r}(X_1+b, X_2, \dots, X_{p - \ell + 1})$
    at the end of the computation.
    \begin{align*}
        &f(q(n_1, \dots, n_p))\\
        &\eqdef 
        \sum_{v_1 \dots v_{k+1} = q(n_1, \dots, n_p)}
        \pi(\mu(v_1), \dots, \mu(v_{k+1})) \\
        &= \sum_{(\ell, b, r)}
           \sum_{v_2 \dots v_{k+1} = q_{\ell,r}(n_\ell - b, \dots, n_p)}
           \pi(\mu(s_{\ell,r,b}(n_1, \dots, n_{\ell-1})), \mu(v_2), \dots, \mu(v_{k+1}))
        \\
        &= 
           \sum_{(\ell, 0, r)}
           \sum_{v_2 \dots v_{k+1} = q_{\ell,b,0}(n_\ell - b, \dots, n_p)}
           \pi(m_{\ell,r,0}, \mu(v_2), \dots, \mu(v_{k+1}))
           \\
        &+ 
           \sum_{(\ell, b > 0, r)}
           \sum_{v_2 \dots v_{k+1} = q_{\ell,r}(n_\ell - b, \dots, n_p)}
           \pi(m_{\ell,r,1}, \mu(v_2), \dots, \mu(v_{k+1}))
        \\
        &= 
           \sum_{(\ell, 0, r)}
           \sum_{v_2 \dots v_{k+1} = q_{\ell,b,0}(n_\ell - b, \dots, n_p)}
           \pi_{\ell,r,0}(\mu(v_2), \dots, \mu(v_{k+1}))
           \\
        &+ 
           \sum_{(\ell, b > 0, r)}
           \sum_{v_2 \dots v_{k+1} = q_{\ell,r}(n_\ell-b, \dots, n_p)}
           \pi_{\ell,r,1}(\mu(v_2), \dots, \mu(v_{k+1}))
        \\
        &= 
           \sum_{1 \leq \ell \leq p}
           \sum_{0 \leq r < \omega \times \card{u_\ell}}
           (\pi_{\ell,r,0})^\dagger (q_{\ell, 0, r}(n_\ell-b, \dots, n_p))
           \\
        &+ 
           \sum_{1 \leq \ell \leq p}
           \sum_{0 \leq r < \omega \times \card{u_\ell}}
           \sum_{0 < b < n_\ell}
           (\pi_{\ell,r,1})^{\dagger}(q_{\ell,r}(n_\ell - b, \dots, n_p))
    \end{align*}
    Now, using the induction hypothesis,
    we have \kl{natural binomial functions} $F_{\ell,r,0}$ and $F_{\ell,r,1}$
    satisfying 
    \begin{equation*}
       (\pi_{\ell,r,1})^{\dagger}(q_{\ell,r}(n_\ell - b, \dots, n_p))
       = F_{\ell,r,1}(\omega (n_\ell - b), \dots, \omega n_p)
       \quad 
       \forall n_\ell - b, \dots, n_p \geq 1
       \quad .
   \end{equation*}
   And similarly
    \begin{equation*}
        (\pi_{\ell,r,0})^{\dagger}(q_{\ell,r}(n_1, \dots, n_{\ell-1})
        = F_{\ell,r,0}(\omega n_1, \dots, \omega n_{\ell-1})
       \quad 
       \forall n_1, \dots, n_{\ell - 1} \geq 1
       \quad .
   \end{equation*}

   It is a well-known equality that for all $s,n \in \Nat$,
   $\sum_{0 < i < n} \binom{s}{i} = \binom{s+1}{n}$.
   As a consequence, \kl{natural binomial functions} are
   stable under the following summation operation:
   $\Sigma_Y \colon Q(x_1,\dots,x_n,y) \mapsto \sum_{0 < b < y} Q(x_1, \dots, x_n, b)$.
   This allows us to conclude by defining:
   \begin{equation*}
       F(x_1, \dots, x_p) \defined
       \sum_{1 \leq \ell \leq p} \sum_{0 \leq r < \omega \card{u_\ell}}
       F_{l,r,0}(x_{\ell}, \dots, \omega x_p) + \Sigma_Y F_{l,r,1}(Y,
       x_{\ell+1}, \dots, x_p)
       \quad .
   \end{equation*}
   The latter being a \kl{natural binomial function} satisfying
   the desired equality.

\end{proof}

@@

Let us also address the fact that the distinction between \kl{natural binomial
functions} and \kl{natural binomial polynomials} vanishes when we are
interested in polynomials. As a consequence, to a \kl{natural binomial
function} corresponds exactly one \kl{natural binomial polynomial} that
coincides with it on sufficiently large inputs (\cref{natural-binomial-polynomial:lem})
which allows us to conclude that \kl{$\Nat$-rational polynomials} are in
$\CorrectPoly$ (\cref{n-rat-correct:lem}).

\begin{lemma}
    \label{natural-binomial-polynomial:lem}
    Let $P \in \Rat[X_1, \dots, X_k]$ be a polynomial,
    $\ell \in \Nat$, 
    and let $f$ 
    be a 
    \kl{natural binomial function} such that
    $P = f$ over $(\Nat_{\geq \ell})^n$. If
    $f(x_1, \dots, x_k) = \sum_{i = 1}^n n_i 
    \prod_{j = 1}^k \binom{x_j - p_{i,j}}{k_{i,j}}$,
    then
    $P =
    \sum_{i = 1}^n n_i 
    \prod_{j = 1}^k \pbinom{X_j - p_{i,j}}{k_{i,j}}$.
\end{lemma}
\begin{proof}
    Let $m$ be the maximal value of all $p_{i,j}$, $k_{i,j}$, and $\ell$.
    Over $(\Nat_{\geq 2m})^k$, $f$ coincides with
    the desired polynomial. Now, because $f$,$P$, and the desired
    polynomial coincide
    over a large enough subset of $\Nat^k$,
    this means that $P$ has the desired shape.
\end{proof}

\begin{corollary}
    \label{n-rat-correct:lem}
    Let $P \in \Rel[X_1, \dots, X_p]$ be an \kl{$\Nat$-rational polynomial}.
    Then,
    $P \in \CorrectPoly$.
\end{corollary}
\begin{proof}
    Let $f$ be the \kl{commutative}
    \kl{$\Nat$-polyregular function}
    with domain defined as $\Sigma \defined \set{a_1, \dots, a_p}$
    that \kl{represents} $P$. 
    Using \cref{n-poly-combinatorics:lem},
    there exists a number $\omega \in \Nat_{\geq 1}$
    and \kl{natural binomial function} $Q$
    such that
    for all $n_1, \dots, n_p \geq 1$:
    \begin{equation*}
        f\left(
            \prod_{i = 1}^p a_i^{\omega n_i}
        \right)
        = Q(n_1, \dots, n_p)
        = P(\omega n_1, \dots, \omega n_p) 
        \quad .
    \end{equation*}
    As a consequence of \cref{natural-binomial-polynomial:lem}, $P(\omega X_1, \dots, \omega X_p)$ equals the corresponding 
    \kl{natural binomial polynomial}.
    Let us remark that the (unique) \kl{maximal monomial} of the 
    \kl{binomial monomial} $\pbinom{X -
    p}{k}$ has coefficient $1/k!$, and is therefore \kl{non-negative}.
    We conclude that
    the \kl{maximal monomials} of 
    $P(\omega X_1, \dots, \omega X_p)$ are \kl{non-negative},
    and since $\omega \geq 1$, we conclude that
    the \kl{maximal monomials} of $P$ have \kl{non-negative} coefficients.

@@

Let us conclude this section by considering polynomials with coefficients in
$\Rat$, and justify that all the combinatorial work has already happened in
$\Rel$ and $\Nat$.

\begin{lemma}
    \label{natural-binomia-correct:lem}
    Let $P$ be a \kl{non-negative} \kl{natural binomial polynomial},
    and let $\alpha$ be such that $\alpha P \in \Rel[\vec{X}]$.
    Then, $\alpha P \in \CorrectPoly$.
\end{lemma}
\begin{proof}
    The only think to remark is that
    $\restr{P}{\nu}$ remains a \kl{natural binomial polynomial}
    for all partial valuations $\nu$, and furthermore remains positive.
\end{proof}

\begin{corollary}
    \label{decide-rat-poly-npoly:cor}
    Let $P \in \Rat[\vec{X}]$ be a polynomial with \emph{rational}
    coefficients and let $\alpha$ be the smallest number in $\Nat_{\geq 1}$
    such that $\alpha P \in \Rel[\vec{X}]$. Then, the following are equivalent:
    \begin{enumerate}
        \item \label{rat-npoly-0:item} $P$ is a \kl{natural binomial polynomial} such that $P(0,\dots,0) \geq 0$,
        \item \label{rat-npoly-1:item} $P$ is a \kl{non-negative} \kl{natural binomial polynomial},
        \item \label{rat-npoly-2:item} $P$ is a \kl{$\Nat$-rational polynomial},
        \item \label{rat-npoly-3:item} $P$ is \kl{represented} by a \kl{star-free $\Nat$-polyregular function},
        \item \label{rat-npoly-4:item} $\alpha P \in \CorrectPoly$,
            and for all $\vec{x} \in \Nat^{\vec{X}}$,
            $P(\vec{x})$ is a multiple of $\alpha$.
    \end{enumerate}
    In particular, the properties are decidable.
\end{corollary}
\begin{proof}
    First, let us remark that 
    \cref{rat-npoly-0:item} $\iff$ \cref{rat-npoly-1:item}
    because \kl{natural binomial polynomials} are increasing.
    Furthermore, \cref{rat-npoly-3:item} $\implies$ \cref{rat-npoly-2:item}
    because $\NSF \subseteq \NPoly$.

    Then, \cref{rat-npoly-4:item} $\implies$ \cref{rat-npoly-3:item}, because
    if $\alpha P \in \CorrectPoly$, then it is an \kl{$\Nat$-rational
    polynomial}. But in particular, there exists a polyregular function $f$
    that represents $\alpha P$ with outputs in $\set{ a }$. Now, let us
    post-compose this function by the one that maps $a^{k \alpha + r}$ to
    $a^{k}$, which is a \kl{polyregular function}. We conclude that $P$ is
    \kl{represented} by an \kl{$\Nat$-polyregular function}.

    We also know that \cref{rat-npoly-2:item} $\implies$
    \cref{rat-npoly-4:item}, since if $P$ is an \kl{$\Nat$-rational
    polynomial}, then so is $\alpha P$, and in particular $\alpha P \in
    \CorrectPoly$ by \cref{corrected-version:thm}.

    As a consequence, we have proven that \cref{rat-npoly-0:item} $\iff$
    \cref{rat-npoly-1:item} and \cref{rat-npoly-2:item} $\iff$
    \cref{rat-npoly-3:item} $\iff$ \cref{rat-npoly-4:item}.

    Finally, \cref{rat-npoly-1:item} $\implies$ \cref{rat-npoly-4:item} is
    exactly \cref{natural-binomia-correct:lem}. And \cref{rat-npoly-3:item}
    $\implies$ \cref{rat-npoly-1:item} is obtained
    by combining \cref{n-sf-combinatorics:lem} and \cref{natural-binomial-polynomial:lem}.
\end{proof}

\AP Notice that we can also fully characterize polynomials that can be computed
using \kl{$\Rel$-rational series}, as they are precisely those computable by a
difference of two \kl{$\Nat$-rational polynomials}. This drives us to introduce
the class of \intro{integer binomial polynomials}, which are obtained by
$\Rel$-linear combinations of products of \kl{binomial monomials} of the form
$\pbinom{X - p}{k}$ for some $k,p \in \Nat$.

\begin{corollary}
    \label{integer-binomial-polynomials:cor}
    Let $P \in \Rat[\vec{X}]$. Then, $P$ is a \kl{$\Rel$-rational polynomial}
    if and only if $P$ is an \kl{integer binomial polynomial}.
\end{corollary}
\begin{proof}
    Let $f = f_+ - f_-$ where both $f_+$ and $f_-$ are 
    \kl{star-free $\Nat$-polyregular functions}.
    One can apply \cref{n-sf-combinatorics:lem}
    to conclude that $P$ coincides with an 
    \kl{integer binomial polynomial} over large enough inputs,
    hence that $P$ is such a polynomial.
\end{proof}

>>>>

	\textbf{Base case: $k = 1$.}
	Let us show that $f \circ q$ is
	actually a constant (positive) function (and in particular a \kl{natural binomial function}), as for
	all $n_1, \dots, n_p \geq 1$,
	\begin{align*}
		f(q(n_1, \dots, n_p))
		 & \eqdef \pi\left(\mu(q(n_1, \dots, n_p))\right)                                      \\
		 & \eqdef \pi\left(\mu(\alpha_0 \prod_{i = 1}^p u_i^{\omega n_i} \alpha_i)\right)
		\\
		 & = \pi\left(\mu(\alpha_0) \prod_{i = 1}^p \mu(u_i)^{\omega n_i} \mu(\alpha_i)\right)
		 & \text{ morphism }
		\\
		 & = \pi\left(\mu(\alpha_0) \prod_{i = 1}^p \mu(u_i) \mu(\alpha_i)\right)
		 & \text{ idempotent and } n_i \geq 1                                                  \\
		 & = c \geq 0
	\end{align*}

@@

	With all of this preliminary work done, we are now ready to conclude by
	simply unrolling the definition of
	a function
	$f$ defined using a \kl{production function}
	$\pi \colon M^{k+1} \to \Nat$.
	In the following equations, we omit the precise
	range for the sum over $(\ell, r, b)$ to save space.
	Similarly, we will use
	$q_{\ell,r}(X_1, \dots, X_{p-\ell+1})
		\defined q_{\ell,r}(X_1+b, X_2, \dots, X_{p - \ell + 1})$
	at the end of the computation.
	\begin{align*}
		 & f(q(n_1, \dots, n_p))           \\
		 & \eqdef
		\sum_{v_1 \dots v_{k+1} = q(n_1, \dots, n_p)}
		\pi(\mu(v_1), \dots, \mu(v_{k+1})) \\
		 & = \sum_{(\ell, b, r)}
		\sum_{v_2 \dots v_{k+1} = q_{\ell,r}(n_\ell - b, \dots, n_p)}
		\pi(\mu(s_{\ell,r,b}(n_1, \dots, n_{\ell-1})), \mu(v_2), \dots, \mu(v_{k+1}))
		\\
		 & =
		\sum_{(\ell, 0, r)}
		\sum_{v_2 \dots v_{k+1} = q_{\ell,b,0}(n_\ell - b, \dots, n_p)}
		\pi(m_{\ell,r,0}, \mu(v_2), \dots, \mu(v_{k+1}))
		\\
		 & +
		\sum_{(\ell, b > 0, r)}
		\sum_{v_2 \dots v_{k+1} = q_{\ell,r}(n_\ell - b, \dots, n_p)}
		\pi(m_{\ell,r,1}, \mu(v_2), \dots, \mu(v_{k+1}))
		\\
		 & =
		\sum_{(\ell, 0, r)}
		\sum_{v_2 \dots v_{k+1} = q_{\ell,b,0}(n_\ell - b, \dots, n_p)}
		\pi_{\ell,r,0}(\mu(v_2), \dots, \mu(v_{k+1}))
		\\
		 & +
		\sum_{(\ell, b > 0, r)}
		\sum_{v_2 \dots v_{k+1} = q_{\ell,r}(n_\ell-b, \dots, n_p)}
		\pi_{\ell,r,1}(\mu(v_2), \dots, \mu(v_{k+1}))
		\\
		 & =
		\sum_{1 \leq \ell \leq p}
		\sum_{0 \leq r < \omega \times \card{u_\ell}}
		(\pi_{\ell,r,0})^\dagger (q_{\ell, 0, r}(n_\ell-b, \dots, n_p))
		\\
		 & +
		\sum_{1 \leq \ell \leq p}
		\sum_{0 \leq r < \omega \times \card{u_\ell}}
		\sum_{0 < b < n_\ell}
		(\pi_{\ell,r,1})^{\dagger}(q_{\ell,r}(n_\ell - b, \dots, n_p))
	\end{align*}
	Now, using the induction hypothesis,
	we have \kl{natural binomial functions} $F_{\ell,r,0}$ and $F_{\ell,r,1}$
	satisfying
	\begin{equation*}
		(\pi_{\ell,r,1})^{\dagger}(q_{\ell,r}(n_\ell - b, \dots, n_p))
		= F_{\ell,r,1}(\omega (n_\ell - b), \dots, \omega n_p)
		\quad
		\forall n_\ell - b, \dots, n_p \geq 1
		\quad .
	\end{equation*}
	And similarly
	\begin{equation*}
		(\pi_{\ell,r,0})^{\dagger}(q_{\ell,r}(n_1, \dots, n_{\ell-1})
		= F_{\ell,r,0}(\omega n_1, \dots, \omega n_{\ell-1})
		\quad
		\forall n_1, \dots, n_{\ell - 1} \geq 1
		\quad .
	\end{equation*}

	It is a well-known equality that for all $s,n \in \Nat$,
	$\sum_{0 < i < n} \binom{s}{i} = \binom{s+1}{n}$.
	As a consequence, \kl{natural binomial functions} are
	stable under the following summation operation:
	$\Sigma_Y \colon Q(x_1,\dots,x_n,y) \mapsto \sum_{0 < b < y} Q(x_1, \dots, x_n, b)$.
	This allows us to conclude by defining:
	\begin{equation*}
		F(x_1, \dots, x_p) \defined
		\sum_{1 \leq \ell \leq p} \sum_{0 \leq r < \omega \card{u_\ell}}
		F_{l,r,0}(x_{\ell}, \dots, \omega x_p) + \Sigma_Y F_{l,r,1}(Y,
		x_{\ell+1}, \dots, x_p)
		\quad .
	\end{equation*}
	The latter being a \kl{natural binomial function} satisfying
	the desired equality.
\end{proof}

@@

\begin{corollary}
	\label{n-rat-correct:lem}
	Let $P \in \Rel[X_1, \dots, X_p]$ be an \kl{$\Nat$-rational polynomial}.
	Then,
	$P \in \CorrectPoly$.
\end{corollary}
\begin{proof}
	Let $f$ be the \kl{commutative}
	\kl{$\Nat$-polyregular function}
	with domain defined as $\Sigma \defined \set{a_1, \dots, a_p}$
	that \kl{represents} $P$.
	Using \cref{n-poly-combinatorics:lem},
	there exists a number $\omega \in \Nat_{\geq 1}$
	and \kl{natural binomial function} $Q$
	such that
	for all $n_1, \dots, n_p \geq 1$:
	\begin{equation*}
		f\left(
		\prod_{i = 1}^p a_i^{\omega n_i}
		\right)
		= Q(n_1, \dots, n_p)
		= P(\omega n_1, \dots, \omega n_p)
		\quad .
	\end{equation*}
	Let us remark that for large enough values of $X$, the \kl{binomial function}
	$\binom{X - p}{k}$ coincides with a polynomial whose dominant coefficient
	is $1/k!$ which is \kl{non-negative}.
	We conclude that
	the \kl{maximal monomials} of
	$P(\omega X_1, \dots, \omega X_p)$ are \kl{non-negative},
	and since $\omega \geq 1$, we conclude that
	the \kl{maximal monomials} of $P$ have \kl{non-negative} coefficients.

@@

\subsubsection{From $\Rel$ to $\Rat$}

\AP Let us conclude this section by considering polynomials with
coefficients in $\Rat$, and justify that all the combinatorial work has
already happened in $\Rel$ and $\Nat$. A first observation is that from
\cref{n-poly-combinatorics:lem,n-sf-combinatorics:lem}, we know that the
functions that can be computed by \kl{star-free $\Nat$-polyregular
	functions} are going to be suitable combinations of \kl{natural binomial
	functions}. This motivates the following definition of the ``polynomial
counterpart" of a binomial coefficient, $\intro*\pbinom{X - \ell}{k}$
defined as $(X - \ell) \cdots (X - \ell - k) / k!$, that we call a
\intro{binomial monomial}, and introduce \intro{natural binomial
	polynomials} as $\Nat$-linear combinations of products of \kl{binomial
	monomials}, i.e., of the shape: $P(X_1, \dots, X_k) = \sum_{i = 1}^n n_i
	\prod_{j = 1}^k \pbinom{X_j - p_{i,j}}{k_{i,j}}$. Similarly, we introduce
the class of \intro{integer binomial polynomials}, which are obtained by
$\Rel$-linear combinations of products of \kl{binomial monomials}.

\AP
These definitions are motivated by the classical result of Pólya that
characterizes polynomials $P$ in $\Rat[X]$ that \intro{integer-valued} (i.e., are such
that $P(\Rel) \subseteq \Rel$) as \kl{integer binomial polynomials}
\cite{POLYA1915,CACHA1996}, which are often called \emph{Newton Polynomials}. Note
that this result straightforwardly extends to multiple indeterminates as we
prove in \cref{integer-binomial-polynomial:lem}.

\begin{lemma}
	\label{integer-binomial-polynomial:lem}
	Let $P \in \Rat[X_1, \dots, X_k]$ be a polynomial.
	Then, $P$ is an \kl{integer binomial polynomial} if and only if
	$P(\Rel^k) \subseteq \Rel$.
\end{lemma}
\begin{proof}
	Let us first notice that $\pbinom{X}{k}$ is \kl{integer valued}
	when $k \in \Nat$. One way to notice this is that when $X \geq 0$,
	$\pbinom{X}{k} = \binom{X}{k}$ is the number of ways to choose $k$ elements among $X$,
	which is an integer. When
	$X < 0$, then $\pbinom{X}{k} = (-1)^k \pbinom{k - X + 1}{k} = (-1)^k \binom{k - X + 1}{k}$
	is also an integer. Because \kl{integer-valued} polynomials are closed under products
	and $\Rel$-linear combination, we conclude that all \kl{integer binomial polynomials} are
	\kl{integer-valued}.

	For the converse direction, we follow the original proof of Pólya \cite{POLYA1915,CACHA1996}.
	The only difference is that we leverage differential operators on multiple indeterminates.
	To that end, let us consider the operator $\Delta_i$ that maps
	a polynomial $P$ to the polynomial $\Delta_i(P) \defined P(X_1, \dots, X_i + 1, \dots, X_k) - P$.
	That is, the discrete partial derivative with respect to the $i$-th indeterminate.
	Let us notice that $\Delta_i \pbinom{X_i}{\alpha} = \pbinom{X_i}{\alpha - 1}$ when $\alpha > 0$,
	indeed:
	\begin{align*}
		\Delta_i \pbinom{X_i}{\alpha} & = \pbinom{X_i + 1}{\alpha} - \pbinom{X_i}{\alpha}                                                         \\
		                              & = \frac{(X_i + 1) \cdots (X_i + 1 - \alpha + 1)}{\alpha!} - \frac{X_i \cdots (X_i - \alpha + 1)}{\alpha!} \\
		                              & = \frac{X_i \cdots (X_i - \alpha + 2)}{\alpha!} \alpha                                                    \\
		                              & = \pbinom{X_i}{\alpha - 1}
		\quad .
	\end{align*}
	Furthermore, when $\alpha = 0$, $\Delta_i \pbinom{X_i}{0} = 0$.

	Let us now remark that a simple expansion proves $\Delta_i \Delta_j P = \Delta_j \Delta_i P$ for all
	$1 \leq i,j \leq k$.
	This justifies the soundness of the notation
	$\Delta_\alpha$ where $\alpha \colon \set{1, \dots, k} \to \Nat$ is a
	multi-index, where $\Delta_{\alpha} \defined \Delta_1^{\alpha_1} \cdots
		\Delta_k^{\alpha_k}$.
	Let us write $\card{\alpha} \defined \sum_{i = 1}^k \alpha_i$ for the
	size of a multi-index.
	We claim that for all $P \in \Rat[X_1, \dots, X_k]$ of degree at most $d$,
	the following \emph{discrete Taylor expansion} holds:
	\begin{equation}
		\label{discrete-taylor:eq}
		P =
		\sum_{\card{\alpha} \leq d}
		\Delta_{\alpha} P (0, \dots, 0)
		\times
		\prod_{i = 1}^k \pbinom{X_i}{\alpha_i}
		\quad .
	\end{equation}

	To obtain \cref{discrete-taylor:eq}, we proceed by induction on the degree $d$.
	When $d = 0$, the result is holds because $P = P(0, \dots, 0)$.
	Assume that the result holds for all polynomials of degree at most $d$.
	Let $P$ of degree at most $d+1$.
	Then, there exists coefficients $\seqof{c_{\alpha}}{\card{\alpha} \leq d+1}$
	in $\Rat$
	such that
	\begin{equation*}
		P = \sum_{\card{\alpha} \leq d+1} c_{\alpha} \prod_{i = 1}^k \pbinom{X_i}{\alpha_i}
		\quad .
	\end{equation*}
	This is because the monomials of the form $\prod_{i = 1}^k \pbinom{X_i}{\alpha_i}$
	form a basis of $\Rat[X_1, \dots, X_k]$.
	In particular, when applying one partial derivative, one can leverage the induction hypothesis to obtain:
	\begin{align*}
		\Delta_1 P & = \sum_{\card{\alpha} \leq d+1} c_{\alpha} \Delta_1 \prod_{i = 1}^k \pbinom{X_i}{\alpha_i}
		=
		\sum_{\card{\alpha} \leq d+1 \wedge \alpha_1 > 0} c_{\alpha}  \pbinom{X_1}{\alpha_1 - 1} \prod_{i = 2}^k \pbinom{X_i}{\alpha_i}
		\\
		           & = \sum_{\card{\beta} \leq d} \Delta_{\beta}(\Delta_1 P)(0,\dots,0) \times \pbinom{X_1}{\beta_1} \prod_{i = 2}^k \pbinom{X_i}{\beta_i}
		\quad .
	\end{align*}

	Using again the fact that the monomials form a basis, we conclude by
	identification that for all $\card{\alpha} \leq d+1$ such that $\alpha_1 >
		0$, we have $c_{\alpha} = \Delta_{\alpha}P (0,\dots,0)$. We can repeat the
	same process with $\Delta_i$ for $1 \leq i \leq k$ to obtain that
	$c_{\alpha} = \Delta_{\alpha} P (0,\dots, 0)$ for all $\alpha$ such that $1
		\leq \card{\alpha} \leq d+1$. Now, for the specific case of $\card{\alpha}
		= 0$, which is the constant term of $P$, we simply conclude that
	$P(0,\dots,0) = c_{\alpha}$, and notice that $\Delta_{\alpha} P = P$ in
	this case.

	Let us now conclude by noticing that if $P$ is \kl{integer-valued},
	then so is $\Delta_i P$ for all $1 \leq i \leq k$. As a consequence,
	so are $\Delta_{\alpha} P$, for all multi-indexes $\alpha$, and we conclude
	that $\Delta_{\alpha}P (0,\dots,0) \in \Rel$ for all $\alpha$.
	Combined with \cref{discrete-taylor:eq}, we conclude that $P$ is an \kl{integer binomial polynomial}.
\end{proof}

As an immediate corollary, we completely characterize the class of
polynomials with rational coefficients that can be computed by
\kl{star-free $\Nat$-polyregular functions}.

\begin{corollary}
	\label{integer-binomial-polynomials:cor}
	Let $P \in \Rat[\vec{X}]$, and let $\alpha$ be the minimal number in $\Nat$ such that
	$\alpha P \in \Rel[\vec{X}]$. Then, the following properties are equivalent:
	\begin{enumerate}
		\item \label{int-bin-0:item} $P$ is an \kl{integer binomial polynomial},
		\item \label{int-bin-1:item} $P$ \kl{represented} by a \kl{star-free $\Rel$-polyregular function},
		\item \label{int-bin-2:item} $P$ \kl{represented} by a \kl{$\Rel$-polyregular function},
		\item \label{int-bin-3:item} $P(\Rel^k) \subseteq \Rel$.
	\end{enumerate}
	These properties are furthermore decidable.
\end{corollary}
\begin{proof}
	Let us first note that implications \cref{int-bin-1:item}
	$\implies$ \cref{int-bin-2:item} $\implies$ \cref{int-bin-3:item} are obvious.
	Now, \cref{int-bin-3:item} $\implies$ \cref{int-bin-0:item} is a direct
	consequence of \cref{integer-binomial-polynomial:lem}.
	Finally, \cref{int-bin-0:item} $\implies$ \cref{int-bin-1:item} follows from the fact
	that $\pbinom{X - p}{k}$ is \kl{represented} by a \kl{star-free $\Rel$-polyregular function}
	defined by hardcoding the output values (in $\Rel$) when $0 \leq X \leq p$, and
	using a \kl{star-free $\Nat$-polyregular function} when $X > p$
	(\cref{binomial-function-star-free:lem}).
	Because
	$\ZSF$ is closed under products and $\Rel$-linear combinations, we conclude.
\end{proof}

Obtaining an analogue of \cref{integer-binomial-polynomials:cor}
for \kl{$\Nat$-polyregular functions} is more challenging. The
naïve approach would be to consider some variation around \kl{natural binomial
	polynomials}. A first observation is that the class of products of the form
$\prod_{i = 1}^n \pbinom{X_i - p_i}{k_i}$ is a generating family for
$\Rat[\vec{X}]$ but is not linearly independent. As a consequence, there may be
several ways to write a given polynomial, and as illustrated by
\cref{natural-binomial-polynomial-basis:ex}, some of them will
exhibit negative coefficients.\footnote{This was not a problem for \kl{integer
		binomial polynomials}, for which the change of basis mapped coefficients in
	$\Rel$ to coefficients $\Rel$.} Furthermore, there are some \kl{natural
	binomial polynomials} that take negative values on positive inputs, as
illustrated by \cref{natural-binomial-polynomial-negative:ex}.
Finally, restricting our attention to \kl{non-negative} \kl{natural binomial
	polynomials} suffers from the same kind of issues as
\cref{karh:thm},
witnessed by \cref{natural-binomial-polynomial-positive-bad:ex}.

\begin{example}
	\label{natural-binomial-polynomial-negative:ex}
	The polynomial $\pbinom{X - 2}{2}$ takes negative values for $X = 0$.
\end{example}

\begin{example}
	\label{natural-binomial-polynomial-basis:ex}
	The polynomial $\pbinom{X - 2}{2} + 1$ is a \kl{non-negative} \kl{natural binomial polynomial}
	but in the standard basis, it is written
	$\pbinom{X}{2} - \pbinom{X}{1} + 2$, which has a negative coefficient.
\end{example}

\begin{example}
	\label{natural-binomial-polynomial-positive-bad:ex}
	The polynomial
	$Q(X,Y,Z) \defined \pbinom{X - 4}{1} \pbinom{Y}{1} \pbinom{Z}{1}
		+ 8 \pbinom{Y}{2} + 8 \pbinom{Z}{2} + 4$
	is a \kl{non-negative} \kl{natural binomial polynomial},
	but cannot be computed by a \kl{star-free $\Nat$-polyregular function}.
\end{example}

\AP We say that a \kl{natural binomial polynomial} is \intro{in base $K$} if
all its \kl{binomial monomials} are of the form $\pbinom{X - K}{d}$ for some $d
	\in \Nat$. To address the issues raised by the previous examples, we introduce
the notion of \intro{strongly natural binomial polynomials} \kl{in base $K$},
as the polynomials $P \in \Rat[X]$ such that for all partial valuation $\nu
	\colon \topartial \set{0, \dots, K}$, $\restr{P}{\nu}$ is a \kl{natural
	binomial polynomial} \kl{in base $K$}. This leads to the following
characterization.

\begin{corollary}
	\label{decide-rat-poly-npoly:cor}
	Let $P \in \Rat[\vec{X}]$ be a polynomial with \emph{rational}
	coefficients and let $\alpha$ be the smallest number in $\Nat_{\geq 1}$
	such that $\alpha P \in \Rel[\vec{X}]$. Then, there exists a
	computable $K \in \Nat$, such that the following are equivalent:
	\begin{enumerate}
		\item \label{rat-npoly-1:item}
		      $P$ is a \kl{strongly natural binomial polynomial} \kl{in base $K$},
		\item \label{rat-npoly-2:item} $P$ is \kl{represented} by a \kl{$\Nat$-polyregular function},
		\item \label{rat-npoly-3:item} $P$ is \kl{represented} by a \kl{star-free $\Nat$-polyregular function},
		\item \label{rat-npoly-4:item} $\alpha P \in \CorrectPoly$,
		      and for all $\vec{x} \in \Nat^{\vec{X}}$,
		      $P(\vec{x})$ is a multiple of $\alpha$.
	\end{enumerate}
	In particular, the properties are decidable.
\end{corollary}
\begin{proof}
	First, \cref{rat-npoly-4:item} $\implies$ \cref{rat-npoly-3:item}, because
	if $\alpha P \in \CorrectPoly$, then it is an \kl{$\Nat$-rational
		polynomial}. But in particular, there exists a polyregular function $f$
	that represents $\alpha P$ with outputs in $\set{ a }$. Now, let us
	post-compose this function by the one that maps $a^{k \alpha + r}$ to
	$a^{k}$, which is a \kl{polyregular function}. We conclude that $P$ is
	\kl{represented} by an \kl{$\Nat$-polyregular function}.

	We also know that \cref{rat-npoly-2:item} $\implies$
	\cref{rat-npoly-4:item}, since if $P$ is an \kl{$\Nat$-rational
		polynomial}, then so is $\alpha P$, and in particular $\alpha P \in
		\CorrectPoly$ by \cref{corrected-version:thm}.
\end{proof}
